### 2009-04-06 talk/icooolps2009-dotnet/benchmarks.tex
adapt che conclusions to the new paper
move the benchmarks to my home dir on codespeak, and add a link to jsr-292

  http://codespeak.net/svn/pypy/extradoc/talk/ecoop2009/benchmarks/}

@@

As already discussed, our generated JIT does not compile the whole function at
once. Instead, it compiles and executes code chunk by chunk, waiting until it
knows enough informations to generate highly efficient code.  In particular,
at the time it emits the code for the inner loop it exactly knows the
type of \lstinline{obj}, thus it can remove the overhead of dynamic dispatch
and inline the method call.  Moreover, since \lstinline{obj} never escapes the
function, it is \emph{virtualized} and its field \lstinline{value} is stored
as a local variable.  As a result, the generated code turns out to be a simple loop
doing additions in-place.

>>>>

  \texttt{http://codespeak.net/~antocuni/tlc-benchmarks/}}

@@

As already discussed, our generated JIT does not compile the whole function at
once. Instead, it compiles and executes code chunk by chunk, waiting until it
knows enough informations to generate highly efficient code.  In particular,
at the time it emits the code for the inner loop it exactly knows the
type of \lstinline{obj}, thus it can remove the overhead of dynamic dispatch
and inline the method call.  Moreover, since \lstinline{obj} never escapes the
function, the allocation is avoided and its field \lstinline{value} is stored
as a local variable.  As a result, the generated code turns out to be a simple loop
doing additions in-place.

### 2009-04-06 talk/icooolps2009-dotnet/conclusion.tex
move the benchmarks to my home dir on codespeak, and add a link to jsr-292

In particular, the \emph{Da Vinci Machine
  Project} \footnote{\texttt{http://openjdk.java.net/projects/mlvm/}} is exploring and
implementing new features to ease the implementation of dynamic languages on
top of the JVM: some of these features, such as the new
\emph{invokedynamic}\footnote{XXX} instruction and the \emph{tail call
  optimization} can probably be exploited by a potential JVM backend to
generate even more efficient code.

>>>>

In particular, the \emph{Da Vinci Machine
  Project} \footnote{\texttt{http://openjdk.java.net/projects/mlvm/}} is exploring and
implementing new features to ease the implementation of dynamic languages on
top of the JVM: some of these features, such as the new
\emph{invokedynamic}\footnote{\texttt{http://jcp.org/en/jsr/detail?id=292}} instruction and the \emph{tail call
  optimization} can probably be exploited by a potential JVM backend to
generate even more efficient code.
